MS_CNuptake.Rmd

### 2023-05-10 MS_CNuptake.Rmd
separate npp and nmin dataset

#input NPP file
NPP_all <- read.csv("~/data/NPP_Yunke/NPP_Nmin_dataset_with_predictors.csv")

>>>>

#input NPP and nmin file and combine
npp_dataset <- read.csv("~/data/NPP_Yunke/NPP_dataset.csv")
nmin_dataset <- read.csv("~/data/Nmin_Finzi/Nmin_dataset.csv")
NPP_all <- dplyr::bind_rows(npp_dataset, nmin_dataset)
